\textsc{Ferret Miner}: A Process Mining Case Study${}^\dagger$\thanks{${}^\dagger$~Github: \texttt{https://github.com/Martin-Chivo/CMPE255-Team8}; Google Drive: \texttt{shorturl.at/cgFIP}}

### 2022-12-13 paper/paper.tex
Added link to Github and Google Drive.

\title{\textsc{Ferret Miner}: A Process Mining Case Study}

\author{\IEEEauthorblockN{Martin Alvarez-Lopez${}^1$\thanks{${}^1$ MS Candidate in Software Engineering, San José State University}}
% \IEEEauthorblockA{San José State University}
\and
\IEEEauthorblockN{Carlos Hernandez${}^2$\thanks{${}^2$ MS Candidate in Computer Engineering, San José State University}}
% \IEEEauthorblockA{San José State University}
\and
\IEEEauthorblockN{Hardy Leung${}^3$\thanks{${}^3$ MS Candidate in Artificial Intelligence, San José State University}}
% \IEEEauthorblockA{San José State University}
\and
\IEEEauthorblockN{Divyam Sobti${}^3$}
% \IEEEauthorblockA{San José State University}
}

@@

Nowadays, most organizations use information systems to support
the execution of their business processes, generating significant
amounts of data.
Mainstream information systems, such as Enterprise Resource
Planning (ERP), Work on Management Systems (WMS), and Customer
Relationship Management (CRM), have become vital tools behind the
operation of almost 
any company process\cite{Tuto2022}. All of these platforms
offer rich event logging capabilities, in which
an event log is
basically a record of an activity performed with a timestamp embedded
\cite{Proc2022}.

@@

In our process mining case study, we investigated
a dataset with
real-life event log data from the travel reimbursement process at
Eindhoven University of Technology (ETU/e). Through analyzing the event
logs and mining the business process underlying the events, we seek to
identify and suggest remedy to address deficiencies in the reimbursement
process.
The event logs provide a detailed record of the travel reimbursement process,
including important attributes such as identification, resource,
timestamp, permits, payment and budgetting information, and event labels.
Students or staff would submit their reimbursement application,
provide suppport documentation (if traveling internationally), wait for
reimbursement decision and subsequent payment, and possibly deal with
rejection and resubmission. All of these information is captured in the
event log.
Collectively, these information provided a substantial amount of detail
into the process. 
The data was obtained from 
the annual BPI Challenge as part of
the 2020 International Conference on Process Mining \cite{BPI2020}.

@@

\begin{table}[htbp]
\caption{XES Event Attributes (5 Total)}
\vspace{-1em}
\begin{center}
\begin{verbatim}
  XES Event Attributes (5 Total)
    ---------------------------------------------------------
    id, org:resource, concept:name, time:timestamp, org:role
    ---------------------------------------------------------

@@

Perhaps due to prior inconsistency between
versions of the enterprise software, there are fields that are similar
or duplicate of each other. For example, \texttt{Permit ID}, \texttt{Permit id},
and \texttt{Permit travel permit number} are one and the same.
Moreover, it is quite likely that exactly one of the three fields were
filled, while the others are missing (or reported as
\textsc{MISSING}. We combined these similar fields into one, picking out
the value from the non-missing column, and dropped the duplicates. Note that 
we performed this duplicate analysis prior to future treatment of missing
values.

@@

\begin{figure*}[htbp]
\centerline{\includegraphics[width=0.65\textwidth]{images/domestic.png}}
\caption{\textsc{dfg} Model for Domestic Reimbursement.}
\label{fig-domestic}
\end{figure*}

\begin{figure*}[htbp]
\centerline{\includegraphics[width=0.65\textwidth]{images/international.png}}
\caption{\textsc{dfg} Model for International Reimbursement.}
\label{fig-international}
\end{figure*}

@@

This can be done with a method called token-based replay (\textsc{tbr}) on the
\textsc{petri net} converted from the process model. For each trace, we would try
to see if it can be simulated on the \textsc{petri net} which can be done
precisely in a mathematically sound
way. We define the total fitness
simply as the percentage of traces that fit the model. Other techniques
we can apply are 
alignment analysis and behavior analysis, though
they both come at the expense of higher runtime complexity.
Together these techniques can be used to better identify the hows and whys of
non-conformance, and to build better models.
In conformance analysis,
tetting to 100\% total fitness is not a desired goal, as explained earlier.
Instead, what we seek is a tradeoff. On the one hand, you want the model
to be robust enough to elegantly explain the process. On the other hand,
we do not want to over-build a model so complex that it is impossible to
reason about.

>>>>

\title{\textsc{Ferret Miner}: A Process Mining Case
Study${}^\dagger$\thanks{${}^\dagger$~Github: \texttt{https://github.com/Martin-Chivo/CMPE255-Team8}; Google Drive: \texttt{shorturl.at/cgFIP}}}

\author{\IEEEauthorblockN{Martin Alvarez-Lopez${}^1$\thanks{${}^1$~MS Candidate in Software Engineering, San José State University}}
% \IEEEauthorblockA{San José State University}
\and
\IEEEauthorblockN{Carlos Hernandez${}^2$\thanks{${}^2$ MS Candidate in Computer Engineering, San José State University}}
% \IEEEauthorblockA{San José State University}
\and
\IEEEauthorblockN{Hardy Leung${}^3$\thanks{${}^3$ MS Candidate in Artificial Intelligence, San José State University}}
% \IEEEauthorblockA{San José State University}
\and
\IEEEauthorblockN{Divyam Sobti${}^3$}
% \IEEEauthorblockA{San José State University}
}

@@

Nowadays, most organizations use information systems to support
the execution of their business processes, generating significant
amounts of data.
Mainstream information systems, such as Enterprise Resource
Planning (\textsc{erp}), Work on Management Systems (\texttt{wms}), and Customer
Relationship Management (\textsc{crm}), have become vital tools behind the
operation of almost 
any company process\cite{Tuto2022}. All of these platforms
offer rich event logging capabilities, in which
an event log is
basically a record of an activity performed with a timestamp embedded
\cite{Proc2022}.

@@

In our process mining case study, we investigated
a dataset with
real-life event log data from the travel reimbursement process at
Eindhoven University of Technology (ETU/e). Through analyzing the event
logs and mining the business process underlying the events, we seek to
identify and suggest remedy to address deficiencies in the reimbursement
process.
The event logs provide a detailed record of the travel reimbursement process,
including important attributes such as identification, resource,
timestamp, permits, payment and budgetting information, and event labels.
Students or staff would submit their reimbursement application,
provide suppport documentation (if traveling internationally), wait for
reimbursement decision and subsequent payment, and possibly deal with
rejection and resubmission. All of these information is captured in the
event log.
Collectively, these information provided a substantial amount of detail
into the process. 
The data was obtained from 
the annual \textsc{bpi} Challenge as part of
the 2020 International Conference on Process Mining \cite{BPI2020}.

@@

\begin{table}[htbp]
\caption{XES Attributes for Events, and Domestic and Int'l Cases}
\vspace{-1em}
\begin{center}
\begin{verbatim}
  XES Event Attributes (5 Total)
    ---------------------------------------------------------
    id, org:resource, concept:name, time:timestamp, org:role
    ---------------------------------------------------------

@@

Perhaps due to prior inconsistency between
versions of the enterprise software, there are fields that are similar
or duplicate of each other. For example, \texttt{Permit ID}, \texttt{Permit id},
and \texttt{Permit travel permit number} are one and the same.
Moreover, it is quite likely that exactly one of the three fields were
filled, while the others are missing (or reported as
\textsc{missing}. We combined these similar fields into one, picking out
the value from the non-missing column, and dropped the duplicates. Note that 
we performed this duplicate analysis prior to future treatment of missing
values.

@@

\begin{figure*}[htbp]
\centerline{\includegraphics[width=0.55\textwidth]{images/domestic.png}}
\caption{\textsc{dfg} Model for Domestic Reimbursement.}
\label{fig-domestic}
\end{figure*}

\begin{figure*}[htbp]
\centerline{\includegraphics[width=0.55\textwidth]{images/international.png}}
\caption{\textsc{dfg} Model for International Reimbursement.}
\label{fig-international}
\end{figure*}

@@

This can be done with a method called token-based replay (\textsc{tbr}) on the
\textsc{petri net} converted from the process model. For each trace, we would try
to see if it can be simulated on the \textsc{petri net} which can be done
precisely in a mathematically sound
way. We define the total fitness
simply as the percentage of traces that fit the model. Other techniques
we can apply are 
alignment analysis and behavior analysis, though
they both come at the expense of higher runtime complexity.
Together these techniques can be used to better identify the hows and whys of
non-conformance, and to build better models.
In conformance analysis,
getting to 100\% total fitness is not a desired goal, as explained earlier.
Instead, what we seek is a tradeoff. On the one hand, you want the model
to be robust enough to elegantly explain the process. On the other hand,
we do not want to over-build a model so complex that it is impossible to
reason about.
